---
title: "Data Basics"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Data Basics}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(fig.width = 7, fig.height = 7, fig.path = "figures/", echo = TRUE, warning = FALSE, message = FALSE, comment = NA)
devtools::source_gist("8e6e5dc401e3fc1042ef7a030f9d19c7", filename = "revised_toc.R")
```

```{r, include=FALSE}
if (!require(remotes)) install.packages("remotes")
if (!require(wvsR)) {remotes::install_github("cwendorf/wvsR")}
library(wvsR)
```

## Data Basics

This page provides an overview of the data reference material in `wvsR`, including country coverage, available survey items, and supported cultural dimensions for the EVS/WVS joint dataset.
### Identify Countries

The `wvs_countries()` function lists the available countries and waves. The `wave` argument filters the list to countries that participated in a given wave.

```{r}
wvs_countries()
wvs_countries(wave = 7)
```

A `wvs_countries()` call with a `countries` argument returns the iso, country name, and number of observations for the requested country or countries. The countries list is somewhat flexible with names.

```{r}
wvs_countries(countries = "United States")
wvs_countries(countries = c("USA", "GB"))
wvs_countries("United States")
wvs_countries(c("US", "GB"))
wvs_countries(c("United States", "Great Britain"), wave = 7)
```

### Check Item Availability

Use `wvs_items()` to display available EVS/WVS survey items.

```{r}
wvs_items()
```

Additional argumentssuch as `group`, `vars`, or `columns` can be used to filter or customize the output.

```{r}
wvs_items(group = "Perceptions of life")
wvs_items(
  vars = c("A008", "A165"),
  columns = c("label", "group", "direction", "min", "max")
)
```

### Cultural Dimensions

The package defines cultural dimensions derived directly from EVS/WVS survey
items.

| Group    | Dimension                   | Full Title                             | Description                                                                                |
| -------- | --------------------------- | -------------------------------------- | ------------------------------------------------------------------------------------------ |
| Core     | Tradition                   | Traditional vs Secular-Rational        | Tension between traditional religious/authority-based values and secular-rational outlooks |
| Core     | Survival                    | Survival vs Self-Expression            | Shift from material survival concerns toward self-expression and autonomy                  |
| Main     | Institution                 | Institutional Trust                    | Confidence in political, legal, and social institutions                                    |
| Main     | Moral                       | Moral Permissiveness                   | Acceptance of non-traditional moral norms and lifestyle choices                            |
| Main     | Gender                      | Gender Equality                        | Support for equal rights and roles between genders                                         |
| Main     | Civic                       | Civic Engagement                       | Participation in civic and community-oriented political activities                         |
| Extended | Political                   | Political Engagement                   | Political participation, activism, and engagement in public affairs                        |
| Extended | Social                      | Social Trust                           | Generalized trust in other people and social reliability                                   |
| Extended | Economic                    | Market Orientation                     | Attitudes toward markets, redistribution, and economic liberalism                          |
| Extended | Wellbeing                   | Subjective Wellbeing                   | Self-reported happiness, life satisfaction, and wellbeing                                  |
| Extended | Democracy                   | Liberal Democracy Support              | Support for democratic institutions, norms, and civil liberties                            |
| Dev      | TraditionalSecular          | Traditional vs Secular-Rational        | Dev version of the Tradition dimension, derived from updated items                        |
| Dev      | SurvivalSelfExpression      | Survival vs Self-Expression            | Dev version of the Survival dimension                                                     |
| Dev      | Autonomy                    | Autonomy                               | Contrast-based autonomy construct                                                           |
| Dev      | Postmaterialism             | Postmaterialism                        | Lookup-based postmaterialist score                                                          |
| Dev      | LifeSatisfaction            | Life Satisfaction                      | Subjective life satisfaction measure                                                        |
| Dev      | PersonalAgency              | Personal Agency                        | Agency and control over personal outcomes                                                  |
| Dev      | Religiosity                 | Religiosity                            | Religious beliefs and practices                                                              |
| Dev      | SupernaturalBelief          | Supernatural Belief                    | Belief in supernatural phenomena                                                             |
| Dev      | SexualPermissiveness        | Sexual Permissiveness                  | Acceptance of permissive sexual attitudes                                                    |
| Dev      | EndOfLifePermissiveness     | End-of-life Permissiveness             | Views on permissiveness around end-of-life issues                                           |
| Dev      | CivicMorality               | Civic Morality                         | Moral obligations supporting civic cooperation                                               |
| Dev      | PoliticalParticipation      | Political Participation                | Political participation and related behaviors                                                |
| Dev      | PoliticalInterest           | Political Interest                     | Interest in political affairs                                                                |
| Dev      | InstitutionalTrust          | Institutional Trust                    | Dev version of institutional trust                                                           |
| Dev      | DemocraticValues            | Democratic Values                      | Support for democratic institutions and values                                               |
| Dev      | EconomicIdeology            | Economic Ideology                      | Market orientation and economic attitudes                                                    |
| Dev      | GenderTraditionalism        | Gender Traditionalism                  | Attitudes toward traditional gender roles                                                     |
| Dev      | FilialObligation            | Filial Obligation                      | Duties and obligations toward family                                                         |
| Dev      | FamilyTraditionalism        | Family Traditionalism                  | Traditional family role attitudes                                                             |
| Dev      | Environmentalism            | Environmentalism                       | Environmental concern and pro-environmental attitudes                                       |
| Dev      | WorkEthic                   | Work Ethic                             | Attitudes toward work and its value                                                           |
| Dev      | NationalAttachment          | National Attachment                    | Attachment and sentiment toward the nation                                                   |
| Dev      | GlobalIdentity              | Global Identity                        | Identification with global community                                                          |
| Dev      | ImmigrationAcceptance       | Immigration Acceptance                 | Acceptance of immigrants                                                                      |
| Dev      | GeneralizedTrust            | Generalized Trust                      | Dev version of generalized trust                                                              |
| Dev      | OutgroupTrust               | Outgroup Trust                         | Trust toward outgroups                                                                        |
| Dev      | SecurityOrientation         | Security Orientation                   | Security-related orientations                                                                 |


Use `wvs_dimensions()` to display the defined cultural dimensions and their construction/source information.

```{r}
wvs_dimensions()
```
