---
title: "Custom Dimensions"
output:
  github_document:
    preserve_yaml: FALSE
vignette: >
  %\VignetteIndexEntry{Custom Dimensions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(fig.width = 7, fig.height = 7, fig.path = "figures/", echo = TRUE, warning = FALSE, message = FALSE, comment = NA)
devtools::source_gist("8e6e5dc401e3fc1042ef7a030f9d19c7", filename = "revised_toc.R")
```

```{r, include=FALSE}
if (!require(remotes)) install.packages("remotes")
if (!require(wvsR)) {remotes::install_github("cwendorf/wvsR")}
library(wvsR)
```

## Custom Dimensions

This page shows how to define custom dimensions and use them with the same profile and comparison functions as the default EVS/WVS set.

```{r toc, echo=FALSE}
knitr::current_input() |> revised_toc(base_level = 3, toc_depth = 1)
```

---

### Define A Dimension Set

A dimension set is a named list. Each dimension has a label and a type. 
The items are specified as a character vector of variable names - the codebook 
automatically fills in the response ranges and directions for you.

```{r}
dims_custom <- list(
  SocialProgressivism = list(
    label = "Social Progressivism",
    type = "mean",
    items = c("F118", "F119", "F120", "F121", "F122", "D059", "G052")
  ),
  MarketSkepticism = list(
    label = "Market Skepticism",
    type = "mean",
    items = c("E035", "E036", "E037", "E039", "E033")
  )
)
```

### Validate The Variables

List the items used in each custom dimension so you can verify labels and ranges before using the custom dimensions.

```{r}
wvs_items(
  vars = c("F118", "F119", "F120", "F121", "F122", "D059", "G052")
)
wvs_items(
  vars = c("E035", "E036", "E037", "E039", "E033")
)
```

### Use The Custom Set

Profile a single country using the custom dimensions and plot the result:

```{r, custom-profile}
wvs_profile(
  "JP", 
  dimensions = dims_custom
) |> plot()
```

Compare two countries on the custom dimensions and plot their differences:

```{r, custom-difference}
wvs_difference(
  countries = c("JP", "US"), 
  dimensions = dims_custom
) |> plot()
```

Project countries into the two-dimensional space defined by the selected custom dimensions and highlight the US and JP:

```{r, custom-space}
wvs_space(
  method="dimensions", 
  dimensions = dims_custom, 
  select=c("SocialProgressivism", "MarketSkepticism"),
) |> plot(highlight=c("US", "JP"))
```
