---
title: "Custom Dimensions"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Custom Dimensions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r, include=FALSE}
if (!require(wvsR)) {
  if (!require(remotes)) install.packages("remotes")
  remotes::install_github("cwendorf/wvsR")
}
library(wvsR)
```

## Custom Dimensions

This page shows how to define custom dimensions and use them with the same profile and comparison functions as the default EVS/WVS set.

### Define A Dimension Set

A dimension set is a named list. Each dimension has a label, a description, and
one or more EVS/WVS items. Items declare the source variable, response range,
and direction.

```{r}
custom_dims <- list(
  Social_Short = list(
    label = "Social Trust, Short Form",
    items = list(
      wvs_item("A165", 1, 2, -1),
      wvs_item("G007_34_B", 1, 4, -1),
      wvs_item("G007_35_B", 1, 4, -1),
      wvs_item("G007_36_B", 1, 4, -1)
    )
  )
)
```

### Validate The Variables

The `wvs_variables()` function checks that the source variables exist in the data and reports their labels and observed response ranges.

```{r}
wvs_variables(custom_dims)
```

### Use The Custom Set

The same profile and comparison functions work with custom dimensions.

```{r}
wvs_profile("JP", wave = 7, dimensions = custom_dims)
```

```{r}
wvs_difference(countries = c("JP", "US"), wave = 7, dimensions = custom_dims)
```
