---
title: "Data Definitions"
output:
  github_document:
    preserve_yaml: FALSE
vignette: >
  %\VignetteIndexEntry{Data Definitions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(fig.width = 7, fig.height = 7, fig.path = "figures/", echo = TRUE, warning = FALSE, message = FALSE, comment = NA)
devtools::source_gist("8e6e5dc401e3fc1042ef7a030f9d19c7", filename = "revised_toc.R")
```

```{r, include=FALSE}
if (!require(remotes)) install.packages("remotes")
if (!require(wvsR)) {remotes::install_github("cwendorf/wvsR")}
library(wvsR)
```

## Data Definitions

This page provides an overview of the data reference material in `wvsR`, including country coverage, available survey items, and supported cultural dimensions for the EVS/WVS joint dataset.

```{r toc, echo=FALSE}
knitr::current_input() |> revised_toc(base_level = 3, toc_depth = 1)
```

---

### Identify Countries

The `wvs_countries()` function lists the available countries and waves. The `wave` argument filters the list to countries that participated in a given wave.

```{r}
wvs_countries()
wvs_countries(wave = 7)
```

A `wvs_countries()` call with a `countries` argument returns the iso, country name, and number of observations for the requested country or countries. The countries list is somewhat flexible with names.

```{r}
wvs_countries(countries = c("USA", "GB"))
wvs_countries(c("United States", "Great Britain"))
```

### Check Item Availability

Use `wvs_items()` to display available EVS/WVS survey items. Additional arguments such as `group`, `vars`, or `columns` can be used to filter or customize the output.

```{r}
wvs_items(
  group = "Perceptions of life",
  vars = c("A001", "A002", "A003", "A004", "A005"),
  columns = c("label", "direction", "min", "max")
)
```

### Cultural Dimensions

Use `wvs_dimensions()` to display the defined cultural dimensions and their construction/source information.

```{r}
wvs_dimensions()
```
