---
title: "Cultural Distances"
output:
  github_document:
    preserve_yaml: FALSE
vignette: >
  %\VignetteIndexEntry{Cultural Distances}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(fig.width = 7, fig.height = 7, fig.path = "figures/", echo = TRUE, warning = FALSE, message = FALSE, comment = NA)
devtools::source_gist("8e6e5dc401e3fc1042ef7a030f9d19c7", filename = "revised_toc.R")
```

```{r, include=FALSE}
if (!require(remotes)) install.packages("remotes")
if (!require(wvsR)) {remotes::install_github("cwendorf/wvsR")}
library(wvsR)
```

## Cultural Distances

`wvsR` includes tools for visualising cultural differences across countries. 
These can be used to explore the relationships between dimensions, identify clusters of similar cultures, 
and highlight specific countries of interest.

```{r toc, echo=FALSE}
knitr::current_input() |> revised_toc(base_level = 3, toc_depth = 1)
```

---

## Mapping Countries

`wvs_space()` will provide coordinates for countries directly on two named dimensions. 

```{r}
wvs_space(
  method = "dimensions",
  select = c("Tradition", "Survival")
)
```

Follow with a plot call to visualize the results. It can highlight specific countries.

```{r, distances-space}
wvs_space(
  method = "dimensions",
  select = c("Tradition", "Survival")
) |> plot(highlight = c("US", "CA"))
```

It can also reduce a larger selected dimension space with PCA or MDS.

```{r, distances-pca}
wvs_space(
  method = "pca",
  dimensions = dims_main
) |> plot(highlight = c("US", "CA"))
```

```{r, distances-mds}
wvs_space(
  method = "mds",
  dimensions = dims_all
) |> plot(highlight = c("US", "CA"))
```

## Similar Countries

`wvs_neighbors()` ranks countries by Euclidean distance across the selected dimension means.

```{r}
wvs_neighbors(
  "US",
  n = 5,
  dimensions = dims_main
)
```

It can also be used to find the most similar countries on a single dimension.

```{r}
wvs_neighbors(
  "US",
  n = 10,
  select = c("Economic")
)
```

## Clustering Countries

`wvs_clusters()` applies k-means clustering to the selected country mean profiles.

```{r}
wvs_clusters(
  k = 4,
  dimensions = dims_main
)
```
