---
title: "Cultural Distances"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Cultural Distances}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r, include=FALSE}
if (!require(wvsR)) {
  if (!require(remotes)) install.packages("remotes")
  remotes::install_github("cwendorf/wvsR")
}
library(wvsR)
```

## Cultural Distances

`wvsR` includes tools for visualising cultural differences across countries. 
These can be used to explore the relationships between dimensions, identify clusters of similar cultures, 
and highlight specific countries of interest.

## Similar Countries

`wvs_neighbors()` ranks countries by Euclidean distance across the selected
dimension means.

```{r}
wvs_neighbors(
  "US",
  n = 5,
  dimensions = dims_extended
)
```

```{r}
wvs_neighbors(
  "US",
  n = 5,
  select = c("Tradition", "Survival")
)
```

## Mapping Countries

`wvs_map()` can map countries directly on two named dimensions.

```{r, fig.width = 7, fig.height = 5}
wvs_map(
  method = "dimensions",
  wave = 7,
  select = c("Tradition", "Survival"),
  x_dimension = "Tradition",
  y_dimension = "Survival",
  highlight = c("US", "CA")
)
```

It can also reduce a larger selected dimension space with PCA or MDS.

```{r, fig.width = 7, fig.height = 5}
wvs_map(
  method = "pca",
  dimensions = dims_extended,
  highlight = c("US", "CA")
)
```

```{r, fig.width = 7, fig.height = 5}
wvs_map(
  method = "mds",
  dimensions = dims_extended,
  highlight = c("US", "CA")
)
```

## Clustering Countries

`wvs_clusters()` applies k-means clustering to the selected country mean
profiles.

```{r}
clusters <- wvs_clusters(
  k = 4,
  dimensions = dims_extended,
)

head(clusters$assignments)
clusters$cluster_means
```
