---
title: "Estimation Approach"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Estimation Approach}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(fig.width = 7, fig.height = 7, fig.path = "figures/", echo = TRUE, warning = FALSE, message = FALSE, comment = NA)
devtools::source_gist("8e6e5dc401e3fc1042ef7a030f9d19c7", filename = "revised_toc.R")
```

```{r, include=FALSE}
if (!require(remotes)) install.packages("remotes")
if (!require(wvsR)) {remotes::install_github("cwendorf/wvsR")}
library(wvsR)
```

## Estimation Approach

Most cross-cultural tools report just country scores and leave
the user to judge whether the scores differ meaningfully. `wvsR`
takes a different approach - every quantity is reported as an estimate with
uncertainty.

This means:

- Point estimates (means) are accompanied by confidence intervals.
- Comparisons report the mean difference in the original metric along with
  the CI, not just a significance test.
- Effect sizes (Cohen's d) contextualise how large a difference is relative
  to within-country variability.

### Country Profiles

`wvs_profile()` estimates each selected dimension for one country and returns
the mean, confidence interval, and valid respondent count.
Its default plot overlays respondent-level jittered scores.

```{r}
wvs_profile(
  "US",
  dimensions = dims_extended
)
```

```{r}
wvs_profile(
  "US",
  dimensions = dims_extended
) |> plot()
```

The same function can use specified dimensions instead.

```{r}
wvs_profile(
  "US",
  select = c("Tradition", "Survival")
) |> plot()
```

### Country Comparisons

Use `wvs_compare()` to prepare mean tables separately for the two countries.
It is also useful for comparison plotting and includes respondent-level
jitter points.

```{r}
wvs_compare(
  countries = c("US", "CA"),
  dimensions = dims_extended
)
```

```{r}
wvs_compare(
  countries = c("US", "CA"),
  dimensions = dims_extended
) |> plot()
```

```{r}
wvs_compare(
  countries = c("US", "CA"),
  select = c("Tradition", "Survival")
) |> plot()
```

### Country Differences

`wvs_difference()` estimates the difference between countries on each selected
dimension. Positive values mean the first country scored higher. 

```{r}
wvs_difference(
  countries = c("US", "CA"),
  dimensions = dims_core
)
```

```{r}
wvs_difference(
  countries = c("US", "CA"),
  dimensions = dims_extended
) |> plot()
```

```{r}
wvs_difference(
  countries = c("US", "CA"),
  select = c("Tradition", "Survival")
) |> plot()
```

```{r}
wvs_difference(
  countries = c("US", "CA"),
  dimensions = c(dims_core, dims_main)
)
```
