---
title: "Cultural Estimates"
output:
  github_document:
    preserve_yaml: FALSE
vignette: >
  %\VignetteIndexEntry{Cultural Estimates}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(fig.width = 7, fig.height = 7, fig.path = "figures/", echo = TRUE, warning = FALSE, message = FALSE, comment = NA)
devtools::source_gist("8e6e5dc401e3fc1042ef7a030f9d19c7", filename = "revised_toc.R")
```

```{r, include=FALSE}
if (!require(remotes)) install.packages("remotes")
if (!require(wvsR)) {remotes::install_github("cwendorf/wvsR")}
library(wvsR)
```

## Cultural Estimates

Most cross-cultural tools report just country scores and leave the user to judge whether the scores differ meaningfully. `wvsR` takes a different approach, providing confidence intervals and effect sizes where appropriate.

```{r toc, echo=FALSE}
knitr::current_input() |> revised_toc(base_level = 3, toc_depth = 1)
```

---

### Country Profiles

`wvs_profile()` estimates each selected dimension for one country and returns
the mean, confidence interval, and valid respondent count.

```{r}
wvs_profile(
  "US",
  dimensions = dims_extended
)
```

Follow with a plot call to visualize the results. Its default plot overlays respondent-level jittered scores. (The confidence intervals are not shown in the plot because they are often too small to see.)

```{r, estimation-profile1}
wvs_profile(
  "US",
  dimensions = dims_extended
) |> plot()
```

The same function can use specified dimensions instead.

```{r, estimation-profile2}
wvs_profile(
  "US",
  select = c("Tradition", "Survival")
) |> plot()
```

### Country Comparisons

Use `wvs_compare()` to prepare mean tables separately for the two countries.

```{r}
wvs_compare(
  countries = c("US", "CA"),
  dimensions = dims_extended
)
```

Follow with a plot call to visualize the results. Its default plot overlays respondent-level jittered scores. (The confidence intervals are not shown in the plot because they are often too small to see.)

```{r, estimation-compare1}
wvs_compare(
  countries = c("US", "CA"),
  dimensions = dims_extended
) |> plot()
```

The same function can use specified dimensions instead.

```{r, estimation-compare2}
wvs_compare(
  countries = c("US", "CA"),
  select = c("Tradition", "Survival")
) |> plot()
```

### Country Differences

`wvs_difference()` estimates the difference between countries on each selected
dimension. Positive values mean the first country scored higher. 

```{r}
wvs_difference(
  countries = c("US", "CA"),
  dimensions = dims_core
)
```

Follow with a plot call to visualize the results. Its default plot adds confidence intervals to the mean difference.

```{r, estimation-difference1}
wvs_difference(
  countries = c("US", "CA"),
  dimensions = dims_extended
) |> plot()
```

The same function can use specified dimensions instead.

```{r, estimation-difference2}
wvs_difference(
  countries = c("US", "CA"),
  select = c("Tradition", "Survival")
) |> plot()
```
