---
title: "Estimation Approach"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Estimation Approach}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r, include=FALSE}
if (!require(wvsR)) {
  if (!require(remotes)) install.packages("remotes")
  remotes::install_github("cwendorf/wvsR")
}
library(wvsR)
```

## Estimation Approach

Most cross-cultural tools report just country scores and leave
the user to judge whether the scores differ meaningfully. `wvsR`
takes a different approach - every quantity is reported as an estimate with
uncertainty.

This means:

- Point estimates (means) are accompanied by 95% confidence intervals.
- Comparisons report the mean difference in the original metric along with
  the CI, not just a significance test.
- Effect sizes (Cohen's d) contextualise how large a difference is relative
  to within-country variability.

### Country Profiles

`wvs_profile()` estimates each selected dimension for one country and returns
the mean, 95 percent confidence interval, and valid respondent count.

```{r}
wvs_profile(
  "US",
  dimensions = dims_extended
)
```

```{r}
cp <- wvs_profile(
  "US",
  dimensions = dims_extended
) |> plot()
```

The same function can use specified dimensions instead.

```{r}
wvs_profile(
  "US",
  select = c("Tradition", "Survival")
)
```

### Country Differences

`wvs_difference()` estimates the difference between countries on each selected
dimension. Positive values mean the first country scored higher.

```{r}
wvs_difference(
  countries = c("US", "CA"),
  dimensions = dims_extended
)
```

```{r}
cd <- wvs_difference(
  countries = c("US", "CA"),
  dimensions = dims_extended
) |> plot()
```

```{r}
wvs_difference(
  countries = c("US", "CA"),
  select = c("Tradition", "Survival")
)
```

Use `wvs_compare()` to prepare mean tables separately for the two countries. It is also useful for comparison plotting.

```{r}
wvs_compare(
  countries = c("US", "CA"),
  dimensions = dims_extended
)
```

```{r}
wvs_compare(
  countries = c("US", "CA"),
  dimensions = dims_extended
) |> plot()
```
