---
title: "EVS/WVS Joint Dataset Dev Overview"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{EVS/WVS Joint Dataset Dev Overview}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r, include=FALSE}
if (!require(wvsR)) {
  if (!require(remotes)) install.packages("remotes")
  remotes::install_github("cwendorf/wvsR")
}
library(wvsR)
```

## Overview

`wvsR` provides tools for profiling, comparing, and visualising
cultural differences using data from the European Values Study (EVS) and World
Values Survey (WVS) Joint Dataset. 

### The Six Dimensions

The package defines six cultural dimensions derived directly from EVS/WVS survey
items. All dimensions are scored on a common 0–10 scale (higher = more of the
named construct):

| Dimension        | What it measures                                  |
|:-----------------|:--------------------------------------------------|
| Trust            | Interpersonal trust, fairness, helpfulness        |
| Traditionalism   | Religion, family values, traditional morality     |
| Hierarchy        | Deference to authority, gender-based power        |
| Individualism    | Personal autonomy, independence, self-expression  |
| Tolerance        | Openness to outgroups, minority rights            |
| Civic Engagement | Political and civic participation                 |

To see the full item-level detail:


### Dimension Sets

Dimension definitions are explicit objects. Functions
accept a `dimensions` argument and a `select` argument, which lets the same
scoring engine use the default EVS/WVS set, an extended set, or a user-defined
set.

```{r}
wvs_names(dims_all)
```

### Check Item Availability

The joint v5 file includes all variables used in the development dimension set.
The availability table also reports the source variable description stored in
the `.rdata` object and the observed nonnegative response range.

```{r}
wvs_variables()
```

```{r}
availability <- wvs_variables(dims_all)
subset(
  availability,
  select = c(dimension, variable)
)
```

### Work With Countries and Waves

The `wvs_countries()` function lists the available countries and waves. The `wave` argument filters the list to countries that participated in a given wave.

```{r}
wvs_countries()
wvs_countries(wave = 7)
```

A `wvs_country()` call returns the iso, country name, and number of observations for a given country. The function is flexible with country names.

```{r}
wvs_country("United States")
wvs_country("USA")
wvs_country("US")
```
